How functional traits influence plant growth and shade tolerance across the life-cycle

### 2018-05-01 ms/figure_conceptual.tex
Tweaks for technical check from journal

@@

@@

\newcommand{\ylabel}[2]{
  \node at (#1)[anchor=west, text width=2cm, minimum height=1cm] {
  {\footnotesize #2}};
}

@@

\newcommand{\firstcol}[4]{
  \defineCol{thisrow}{#1}{thiscol}
  \ylabel{$(thiscol) + (-2.1cm,  0cm)$}{#2}
  \plot{  $(thiscol)$                 }{#3}
  \ylabel{$(thiscol) + (0.7cm,   0cm)$}{=}
  \ylabel{$(thiscol) + (1.1cm,   0cm)$}{#4}
}

@@

\defineRow{0}{thisrow}
\rowtitle{Biomass growth}
\firstcol{1}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{\hspace{-1em} \scriptsize $\,\alpha_{\rm \tiny bio} \alpha_{\rm \tiny y}$}{output/conn/net_mass_production_dt_yield}{}
\othercol{3}{\hspace{-1em}$\times\Bigg($\hspace{-0.3em}\scriptsize$A_{\rm l} \bar{p}$}{output/conn/net_mass_production_dt_assimilation}{}
\othercol{4}{\hspace{-1em}-$\Sigma$\scriptsize $M_{\rm i} r_{\rm i}$}{output/conn/net_mass_production_dt_respiration}{\hspace{-0.5em}$\Bigg)$}
\othercol{5}{\hspace{-0.75em}-$\Sigma$\scriptsize $M_{\rm i} k_{\rm i}$}{output/conn/net_mass_production_dt_turnover}{}
\rowlabel{eq:dbdt_2}

\defineRow{1}{thisrow}
\rowtitle{Mass growth}
\firstcol{1}{$\frac{{\rm d}M_{{\rm t}}}{{\rm d}t}$}{output/conn/mass_total_dt_mass_total_dt}{}
\othercol{2}{$\frac{{\rm d}M_{{\rm a}}}{{\rm d}B}$}{output/conn/mass_total_dt_fraction_allocation_growth}{$\times$}
\othercol{3}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/mass_total_dt_net_mass_production_dt}{$+$}
\othercol{4}{$\frac{{\rm d}M_{{\rm h}}}{{\rm d}t}$}{output/conn/mass_total_dt_mass_heartwood_dt}{}
\rowlabel{eq:dMtdt}

@@

\defineRow{3}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_leaf_dt_area_leaf_dt}{}
\othercol{2}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm a}}}$}{output/conn/area_leaf_dt_darea_leaf_dmass_live}{$\times$}
\othercol{3}{$\frac{{\rm d}M_{{\rm a}}}{{\rm d}B}$}{output/conn/area_leaf_dt_fraction_allocation_growth}{$\times$}
\othercol{4}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/area_leaf_dt_net_mass_production_dt}{}
\rowlabel{eq:daldt}

\defineRow{4}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{{\rm d}H}{{\rm d}t}$}{output/conn/height_dt_height_dt}{}
\othercol{2}{$\frac{{\rm d}H}{{\rm d}A_{{\rm l}}}$}{output/conn/height_dt_dheight_darea_leaf}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_leaf_dt_area_leaf_dt}{}
\rowlabel{eq:dhdt}

\defineRow{5}{thisrow}
\rowtitle{Stem-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_stem_dt}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}A_{{\rm b}}}{{\rm d}A_{{\rm l}}}$}{output/conn/area_stem_dt_darea_bark_darea_leaf}{$+$}
\othercol{3}{$\frac{{\rm d}A_{{\rm s}}}{{\rm d}A_{{\rm l}}}$}{output/conn/area_stem_dt_darea_sapwood_darea_leaf}{\hspace{-0.3em}$\Bigg)$}
\othercol{4}{\hspace{-0.4em}$\times\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_leaf_dt}{$+$}
\othercol{5}{$\frac{{\rm d}A_{{\rm h}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_heartwood_dt}{}
\rowlabel{eq:dast}

\defineRow{6}{thisrow}
\rowtitle{Stem-diameter growth}
\firstcol{1}{$\frac{{\rm d}D}{{\rm d}t}$}{output/conn/diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{{\rm d}D}{{\rm d}A_{{\rm st}}}$}{output/conn/diameter_stem_dt_ddiameter_stem_darea_stem}{$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/conn/diameter_stem_dt_area_stem_dt}{}
\rowlabel{eq:dDdt}

>>>>

% \makeatletter
% \newcommand\thefontsize[1]{{#1 The current font size is: \f@size pt\par}}
% \makeatother

@@

% script = 14.4, footnote = 17.28, small = 20.74

% \sffamily
% \thefontsize\scriptsize

@@

\newcommand{\ylabel}[2]{
  \node at (#1)[anchor=west, text width=2cm, minimum height=1cm] {
  \fontsize{19.5pt}{15pt}\selectfont #2};
}

@@

\newcommand{\firstcol}[4]{
  \defineCol{thisrow}{#1}{thiscol}
  \ylabel{$(thiscol) + (-2.1cm,  0cm)$}{#2}
  \plot{  $(thiscol)$                 }{#3}
  \ylabel{$(thiscol) + (0.7cm,   0cm)$}{\footnotesize=}
  \ylabel{$(thiscol) + (1.1cm,   0cm)$}{#4}
}

@@

\defineRow{0}{thisrow}
\rowtitle{Biomass growth}
\firstcol{1}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/net_mass_production_dt_net_mass_production_dt}{}
\othercol{2}{\hspace{-0.8em} \fontsize{14}{10}\selectfont $\alpha_{\rm bio} \alpha_{\rm y}$}{output/conn/net_mass_production_dt_yield}{}
\othercol{3}{\hspace{-1em}{\footnotesize$\times$}$\hspace{-0.1em}\Bigg($\hspace{-0.2em}\fontsize{16}{13}\selectfont $A_{\rm l} \bar{p}$}{output/conn/net_mass_production_dt_assimilation}{}
\othercol{4}{\hspace{-1em}\fontsize{16}{13}\selectfont -$\Sigma M_{\rm i} r_{\rm i}$}{output/conn/net_mass_production_dt_respiration}{\hspace{-0.65em}$\Bigg)$}
\othercol{5}{\hspace{-0.8em}\fontsize{16}{13}\selectfont -$\Sigma M_{\rm i} k_{\rm i}$}{output/conn/net_mass_production_dt_turnover}{}
\rowlabel{eq:dbdt_2}

\defineRow{1}{thisrow}
\rowtitle{Mass growth}
\firstcol{1}{$\frac{{\rm d}M_{{\rm t}}}{{\rm d}t}$}{output/conn/mass_total_dt_mass_total_dt}{}
\othercol{2}{$\frac{{\rm d}M_{{\rm a}}}{{\rm d}B}$}{output/conn/mass_total_dt_fraction_allocation_growth}{\footnotesize$\times$}
\othercol{3}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/mass_total_dt_net_mass_production_dt}{\footnotesize$+$}
\othercol{4}{$\frac{{\rm d}M_{{\rm h}}}{{\rm d}t}$}{output/conn/mass_total_dt_mass_heartwood_dt}{}
\rowlabel{eq:dMtdt}

@@

\defineRow{3}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_leaf_dt_area_leaf_dt}{}
\othercol{2}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}M_{{\rm a}}}$}{output/conn/area_leaf_dt_darea_leaf_dmass_live}{\footnotesize$\times$}
\othercol{3}{$\frac{{\rm d}M_{{\rm a}}}{{\rm d}B}$}{output/conn/area_leaf_dt_fraction_allocation_growth}{\footnotesize$\times$}
\othercol{4}{$\frac{{\rm d}B}{{\rm d}t}$}{output/conn/area_leaf_dt_net_mass_production_dt}{}
\rowlabel{eq:daldt}

\defineRow{4}{thisrow}
\rowtitle{Height growth}
\firstcol{1}{$\frac{{\rm d}H}{{\rm d}t}$}{output/conn/height_dt_height_dt}{}
\othercol{2}{$\frac{{\rm d}H}{{\rm d}A_{{\rm l}}}$}{output/conn/height_dt_dheight_darea_leaf}{\footnotesize$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_leaf_dt_area_leaf_dt}{}
\rowlabel{eq:dhdt}

\defineRow{5}{thisrow}
\rowtitle{Stem-area growth}
\firstcol{1}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_stem_dt}{$\Bigg($}
\othercol{2}{$\frac{{\rm d}A_{{\rm b}}}{{\rm d}A_{{\rm l}}}$}{output/conn/area_stem_dt_darea_bark_darea_leaf}{\footnotesize$+$}
\othercol{3}{$\frac{{\rm d}A_{{\rm s}}}{{\rm d}A_{{\rm l}}}$}{output/conn/area_stem_dt_darea_sapwood_darea_leaf}{\hspace{-0.3em}$\Bigg)$}
\othercol{4}{\hspace{-0.4em}{\footnotesize$\times$}$\frac{{\rm d}A_{{\rm l}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_leaf_dt}{\footnotesize$+$}
\othercol{5}{$\frac{{\rm d}A_{{\rm h}}}{{\rm d}t}$}{output/conn/area_stem_dt_area_heartwood_dt}{}
\rowlabel{eq:dast}

\defineRow{6}{thisrow}
\rowtitle{Stem-diameter growth}
\firstcol{1}{$\frac{{\rm d}D}{{\rm d}t}$}{output/conn/diameter_stem_dt_diameter_stem_dt}{}
\othercol{2}{$\frac{{\rm d}D}{{\rm d}A_{{\rm st}}}$}{output/conn/diameter_stem_dt_ddiameter_stem_darea_stem}{\footnotesize$\times$}
\othercol{3}{$\frac{{\rm d}A_{{\rm st}}}{{\rm d}t}$}{output/conn/diameter_stem_dt_area_stem_dt}{}
\rowlabel{eq:dDdt}
